Fermi and eROSITA bubbles: a proof of concept study

### 2021-12-18 paper.tex
update

\begin{document}
\title{Fermi and eROSITA bubbles}

@@

  We model the external gravity of the Milky Way by prescribing a\
  plane parallel self-gravitating isothermal slab, symmetry about the mid-plane $z=0$,\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

  In our 3D simulation, the Galactic potential can be written as

@@

  where $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is dark logarithmic halo potential,

@@

  is the potential of a plane-parallel isothermal slab mainly contributed by stars within the Galactic plane.

  The steady-state density distribution in a total potential, $\Phi_{\text{total}}$,\
  for the gas can be derived from the isothermal and hydrostatic equilibrium condition,\
  given by
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{, otherwise.}
     \end{cases}
  \end{equation}

@@

  where $\rho_{\text{atmp}}^{\text{peak}}$ can be obtained by assuming that pressure\
  and gravitational potential are continuous at the interface ($z=\pm z_{0}$) between disk and atmosphere.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                           & Description                       & Value                                & Reference                         \\ \midrule
{\bf Potential \& halo}             &                                   &                                      &                                   \\
$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge      & 100 km/s                             & \citep{velocity-dispersion-MW}    \\
$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge     & $4\times 10^{-24}$ g/cm$^{3}$        &                                   \\
$v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \hline
{\bf Atmosphere}                    &                                   &                                      &                                   \\
$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
{\bf Disk}                          &                                   &                                      &                                   \\
$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \midrule
\end{tabular}
\end{table*}

>>>>

\begin{document}
\title{Fermi and eROSITA bubbles: a proof of concept study}

@@

  As a proof-of-concept study, we approximate conventionally axisymmetric potential of Milky Way\
  by a plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

  The plane-parallel potential is fixed throughout our simulations and given by

@@

  where

@@

  is the potential of a isothermal slab mainly contributed by stars within the Galactic plane.

  $\Phi_{\text{halo}}=v^2_{\text{halo}}\ln\left(z^2+d^2_{\text{h}}\right)$\
  is a plane-parallel dark logarithmic halo potential.

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  the steady-state gaseous density distribution in a total potential, $\Phi_{\text{total}}$,\
  can be written as
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{disk}}/m}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}}{k_{B}T_{\text{atmp}}/m}\right] & \text{, otherwise.}
     \end{cases}
  \end{equation}

@@

  All parameters are listed in \Cref{table-parameters}, excpet for $\rho_{\text{atmp}}^{\text{peak}}$ that\
  can be derived from the pressure equilibrium on the interfaces ($|z|=z_{0}$) between disk and atmosphere.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[t]
\centering
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrr@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                           & Description                       & Value                                & Reference                         \\ \midrule
{\bf Disk}                          &                                   &                                      &                                   \\
$z_{0}$                             & Scale height of disk              & 100 pc                               & \citep{peak-ism-density}          \\
$T_{\text{\text{disk}}}$            & Temperature of disk               & $10^{3}$ K                           & \citep{peak-ism-density}          \\
$\rho_{\text{disk}}^{\text{peak}}$  & Peak mass density of disk         & $10^{-23}$ g/cm$^{3}$                & \citep{peak-ism-density}          \\ \hline
{\bf Atmosphere}                    &                                   &                                      &                                   \\
$T_{\text{\text{atmp}}}$            & Temperature of atmosphere         & $10^{6}$ K                           & \citep{temperature-MW}            \\ \hline
{\bf Potential \& halo}             &                                   &                                      &                                   \\
$\sigma_{\text{bulge}}$             & Velocity dispersion of bulge      & 100 km/s                             & \citep{velocity-dispersion-MW}    \\
$\rho_{\text{bulge}}^{\text{peak}}$ & Peak average density of bulge     & $4\times 10^{-24}$ g/cm$^{3}$        &                                   \\
$v_{\text{halo}}$                   &                                   & 131.5 km/s                           & \citep{Johnston1995}              \\
$d_{\text{h}}$                      & Core radius                       & 12 kpc                               & \citep{Johnston1995}              \\ \midrule
\end{tabular}
\end{table*}
